### 2025-08-19 chapters/benchmark.tex
adjusted average scaling per step

\begin{table}[htbp]
\centering
\begin{threeparttable}
\caption{Summary of workload responses to incremental hardware scaling. Positive average values indicate performance improvement per scaling step.}
\label{tab:hardware-impact}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Metric} & \textbf{CPU cores} & \textbf{Memory (MB)} \\
\midrule
Workloads improved                      & 2/6 (33\%) & 2/6 (33\%) \\
Workloads slowed down                   & 1/6 (17\%) & 1/6 (17\%) \\
Workloads unaffected                    & 3/6 (50\%) & 3/6 (50\%) \\
Average performance change per step (\%)& +6.80\%    & +6.80\%    \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item Each increment corresponds to one step increase in CPU cores or memory size.
\item Performance improvements were primarily driven by \texttt{coremark} workloads.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[htbp]
\centering
\begin{threeparttable}
\caption{Summary of workload responses to incremental hardware scaling. Positive average values indicate performance improvement per scaling step.}
\label{tab:hardware-impact}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Metric} & \textbf{CPU cores} & \textbf{Memory (MB)} \\
\midrule
Workloads improved                      & 2/6 (33\%) & 2/6 (33\%) \\
Workloads slowed down                   & 1/6 (17\%) & 1/6 (17\%) \\
Workloads unaffected                    & 3/6 (50\%) & 3/6 (50\%) \\
Average performance change per step (\%)& 9.99   & 9.99   \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item Each increment corresponds to one step increase in CPU cores or memory size.
\item Performance improvements were primarily driven by \texttt{coremark} workloads.
\end{tablenotes}
\end{threeparttable}
\end{table}
